% !TeX spellcheck = en_GB
\chapter{The \Jiben{} \Jianfa{}}\label{ch:jianfa}

The term \Jiben{} \Jianfa{} (\begin{CJK*}{UTF8}{bsmi}基本劍法\end{CJK*}) denotes what is generally referred to as the sword basic techniques or basic cuts.
It may be translated literally as: the \textit{basic}, \textit{elementary}, \textit{fundamental} (\Jiben{}) \textit{methods} (\Fa{}), of the \textit{straight sword} (\Jian{}).

The different styles of \Taijijian{} report a variable number of \Jiben{} \Jianfa{}, usually ranging from four to thirteen or more. The names of several of them are mentioned already in the \JianJing{}, a sword treatise written by \YuDayou{} around 1560, or in the \WubeiZhi{}, a military encyclopaedia presumably published in 1620.
It is not clear though whether these terms were already referring to the very same techniques as they do today in \Taijijian{}, and even more so as the \Jiben{} \Jianfa{} names are not always consistent across styles.

The \Yangjia{} \Michuan{} \Taijijian{} tradition lists eight \Jiben{} \Jianfa{}, each corresponding to one of the eight sections in the \Kunlun{} sword form: \Pi{}, \Ci{}, \Liao{}, \Zha{}, \Mo{}, \Duo{}, \Tiao{}, \Hua{}.
A ninth one, \Dian{}, is also referred to, but is sometimes described as a combination of \Pi{} and \Ci{}, possibly in order to preserve the fit total number of eight pure techniques.
Whatever the reason for it, I have the feeling that this description of \Dian{} as a combination actually acknowledges that the \Jiben{} \Jianfa{} can be mixed together.
I therefore like to consider them not as techniques \textit{per se} but rather as technical principles that, blended together, make up the actual sword techniques. The so-called basic techniques would thus be simply the techniques which are representative  of the \Jiben{} \Jianfa{} constituting their main, yet not exclusive, component. 

A close look at the Chinese characters for the eight \Jianfa{} of the \Yangjia{} \Michuan{} reveals that four of them (\Pi{} \begin{CJK*}{UTF8}{bsmi}劈\end{CJK*}, \Ci{} \begin{CJK*}{UTF8}{bsmi}刺\end{CJK*}, \Duo{} \begin{CJK*}{UTF8}{bsmi}剁\end{CJK*} and \Hua{} \begin{CJK*}{UTF8}{bsmi}劃\end{CJK*}) contain the graphic key for the knife, whereas the others (\Liao{} \begin{CJK*}{UTF8}{bsmi}撩\end{CJK*}, \Zha{} \begin{CJK*}{UTF8}{bsmi}扎\end{CJK*}, \Mo{} \begin{CJK*}{UTF8}{bsmi}抹\end{CJK*}, \Tiao{} \begin{CJK*}{UTF8}{bsmi}挑\end{CJK*}) contain the key for the hand. We may thus argue that the first four focus on how the blade is actually used for cutting or thrusting while the others rather describe the general movement (raising, whipping, etc.) independently of the weapon. As a matter of fact, the \Liao{} and \Zha{} characters can be found in the names of spear, staff or even boxing techniques mentioned in various historical martial arts manuals. The ninth technique, \Dian{} \begin{CJK*}{UTF8}{bsmi}點\end{CJK*}, whose name means \textit{pointing}, is once again an outsider: as its character does not contain the hand or the knife keys, it would exclusively refer to the point of the blade. 

The descriptions of the \Yangjia{} \Michuan{} \Taijijian{} \Jiben{} \Jianfa{} will not  be presented hereafter in their traditional order, which follows the sequence of the corresponding sections in the \Kunlun{} sword form. Instead, I will present first the four blade techniques before proceeding to the other ones. They are personal interpretations allowing for the above points of view and based upon Master Wang's teachings and historical texts. Although the contents of this chapter essentially apply to the \Yangjia{} \Michuan{} tradition, it is expected that they may none the less apply more generally, at least in part, to other styles as well. 

\fiche{
add a table describing the different energies and their scope: Pi is a way of cutting, liao defines the direction of the cut with the true edge and as such can express Pi energy...
Maybe some consideration of the sword and hand keys, correspondence between techniques
}

\input{JibenJianFa_Pi.tex}
\input{JibenJianFa_Hua.tex}
\input{JibenJianFa_Ci.tex}
\input{JibenJianFa_Duo.tex}
\input{JibenJianFa_Liao.tex}
\input{JibenJianFa_Zha.tex}
\input{JibenJianFa_Mo.tex}
\input{JibenJianFa_Tiao.tex}
\input{JibenJianFa_Dian.tex}

\fiche{
\section{What makes a cut effective? }
relaxation, blade alignment
distance
must travel through the target
split or slice

\section{ What makes a thrust effective?}
point control, see pivot points in chapter 2
distance
no need for more than a few centimetres in the target to reach a vital organ
}
